Curation of NYC 311 Request Open Data

### 2023-06-05 talk/slides.Rmd
minor edits to slides

+ Validity check 
    - date (logical check)
    - descriptive fields (drop-down menu)
    - legitimate values
+ Efficiency
    - Eliminate redundant columns
    - Reduce storage with no information loss
+ Feedback: open review for open data

>>>>

+ Validity check 
    - date (logical check)
    - descriptive fields (drop-down menu, possibly multi-step)
    - missing values
    - legitimate values
    - computed fields in the dictionary
+ Efficiency
    - Eliminate redundant columns
    - Reduce storage with no information loss
+ Feedback: open review for open data
